### 2019-11-20 report/02-methods.Rmd
Compute species contribution to the CV, CV_sp and synchrony

habitat_station %<>%
  left_join(flow_temp, by = "station")
```

@@

>>>>

habitat_station %<>%
  left_join(flow_temp, by = "station")
habitat_pressure <- habitat_station
mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
```

@@

### Stability

#### Species contribution

The species contribution to CV and synchrony have been computed, to identify
which species are driving the relationship between CV and species richness.

Species contribution to a metric can be computed as follow:

$$
C_k = CV_{-k} - CV
$$

### 2019-11-20 report/05-stability.Rmd
Compute species contribution to the CV, CV_sp and synchrony

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
```

@@

```{r}
myload(community_metrics, dir = data_common)
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

@@

myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "local_network_build.R"))
# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
  arrange(cv_com)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

@@

## CV, biomass and div (ALREADY DONE!)
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))
```

@@

#### Assembly rules: richness and biomass distribution

```{r}
cv_bm_div_troph_grp %>%
  ggplot(aes(y = cv_st, x = div_st)) +
  geom_point() +
  facet_grid(cols = vars(troph_group))
```

```{r}
sync_com_troph <- net_sp_troph %>%
    rename(species = sp_class) %>%
    filter(troph_group != 1) %>%
    mutate(troph_group = as.factor(troph_group)) %>%
    group_by(troph_group) %>%
    nest() %>%
    mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
    unnest(sync) %>%
    mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
    select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev) %>%
    left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
```

```{r sd-avg-div}
form <- y ~ x
form2 <- y ~ Vmax * x / (Km + x)
form3 <- y ~  a + exp(b * x) 
fit <- stat_poly_eq(
  formula = form2,
  eq.with.lhs = "italic(hat(y))~`=`~",
  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
  parse = TRUE)

ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'nls', formula = form3,
   method.args = list(start = c(a = 0, b = 3)), se = F) +
  #fit +
  facet_grid(cols = vars(troph_group)) +
  #scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- sync_com_troph %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

```{r}

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "local_network_build.R"))
```
```{r}
temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
%>%
  select(station, troph_group, biomass_cv, richness_avg, nbnode_med) %>%
  gather(richness_type, div, richness_avg, nbnode_med) %>%
  ggplot(aes(x = div, y = biomass_cv, color = troph_group)) +
  facet_grid(cols = vars(richness_type), scales = "free_x") +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

The stability of biomass is determined by the standard deviation and the average
biomass of the community.

### Decompose stability

```{r}
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))

cv_bm_div_troph_grp %>%
  ggplot(aes(y = cv_st, x = div_st)) +
  geom_point() +
  facet_grid(cols = vars(troph_group))
```

```{r}
sync_com_troph <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  rename(species = sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
```

```{r}
sync_com_troph %>%
  filter(troph_group != 1) %>%
  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

```{r sd-avg-div}
fit <- stat_poly_eq(
  formula = y ~x,
  eq.with.lhs = "italic(hat(y))~`=`~",
  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
  parse = TRUE)

ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'loess', se = F) +
  #fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- sync_com_troph %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'loess', se = FALSE) +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

```{r, fig.dim = c(7, 14)}
sync_com_troph %>%
  select(troph_group:cv_com, div_st) %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = div_st, y = stab)) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(x = "Trophic species diversity", y = "Stability component") +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
```

```{r, fig.dim = c(10, 7)}
synchrony %>%
  left_join(select(temporal_community_metrics, station, richness_med), by =
    "station") %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_med, y = stab)) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(x = "Species diversity", y = "Stability component") +
  geom_point() +
  facet_grid(rows = vars(comp), scales = "free_y")
```

#### Contribution

```{r}
sync_com_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, species) %>%
  summarise(
    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
    sum_cbt_sync = sum(abs(cbt_sync))
    ) %>%
  arrange(desc(sum_cbt_cv_com)) %>%
  slice(1:10) %>%
  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
  ggplot(aes(y = contrib, x = species)) +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
```

```{r var-cbt, fig.dim = c(10, 7)}
var_cbt <- sync_com_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, station) %>%
  summarise(
    var_cbt_cv_com = var(cbt_cv_com),
    var_cbt_cv_sp = var(cbt_cv_sp),
    var_cbt_sync = var(cbt_sync)
    ) %>%
  gather(comp, contrib, var_cbt_cv_com:var_cbt_sync) %>%
  left_join(select(cv_bm_div_troph_grp, station, troph_group, div_st),
    by = c("station", "troph_group"))

  var_cbt %<>%
    nest() %>%
    mutate(plot = map2(data, troph_group, function(.data, m_title){
	.data %>%
	ggplot(aes(y = contrib, x = div_st)) +
	  geom_point() +
	  scale_x_log10() +
	  facet_wrap(facets = ~comp, scales = "free_y") +
	  labs(title = paste0(m_title))
}
    )
    )

plot_grid(plotlist = var_cbt$plot, ncol = 2)
```

@@

```{r, fig.dim = c(10, 7)}
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

@@

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
  arrange(cv_com)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

@@

## CV, biomass and div (ALREADY DONE!)
```

@@
